Normalized expressions

### 2021-02-24 analysis/normalized.Rmd
More stats

read_csv(normalized_path, col_types = cols(
  minimized = col_character(),
  topcall = col_character(),
  is_model = col_logical(),
  has_fundef = col_logical(),
  has_calls = col_integer(),
  has_assigns = col_integer(),
  has_var = col_logical(),
  has_bracket = col_logical(),
  is_assign = col_logical(),
  is_value = col_logical(),
  is_ignore = col_logical(),
  has_dollar = col_logical(),
  has_user_call = col_logical(),
  has_block = col_logical(),
  normalized = col_character(),
  trimmed = col_character(),
  hash = col_character()
)) -> N

@@

There are `r nb_assign_call_sites` call sites with assignments.

# Polymorphism

@@

it amounts for `r nb_stat_call_sites`.

>>>>

read_csv(normalized_path, col_types = cols(
  minimized = col_character(),
  topcall = col_character(),
  is_model = col_logical(),
  has_fundef = col_logical(),
  has_calls = col_integer(),
  has_assigns = col_integer(),
  has_var = col_logical(),
  has_bracket = col_logical(),
  is_assign = col_logical(),
  is_value = col_logical(),
  is_ignore = col_logical(),
  has_dollar = col_logical(),
  has_user_call = col_logical(),
  has_block = col_logical(),
  has_meta_op = col_logical(),
  normalized = col_character(),
  trimmed = col_character(),
  hash = col_character()
)) -> N

@@

There are `r nb_assigns_call_sites` call sites with assignments.

@@

it amounts for `r nb_stat_call_sites` call sites.

# Substitue&co

`substitute`, `quote` and so on are used to do meta-programming.

```{r}
meta_df <- E_cano %>% filter(has_meta_op)

nb_meta_call_sites <- meta_df %>% pull(src_ref) %>% n_distinct()
```

There are `r nb_meta_call_sites` call sites with `substitute` and `substitute`-like operators.

Are the `substitute` sometimes not placed as a top call?

```{r}
meta_not_top <- meta_df %>% filter(!topcall %in% c("substitute", "quote", "enquote", "bquote"))

nb_m_n_top_call_sites <- meta_not_top %>% pull(src_ref) %>% n_distinct()
```

It happens for `r nb_m_n_top_call_sites` call sites.

# `eval(x[[condition]])` pattern

See https://cran.r-project.org/doc/manuals/r-release/R-lang.html#switch

```{r}
eval_switch <- E_cano %>% filter(has_var, has_bracket, topcall == "[[")

nb_ev_switch_call_sites <- eval_switch %>% pull(src_ref) %>% n_distinct()
```

There are `r nb_ev_switch_call_sites` call sites using that pattern.

But this is actually not correct, because we should look at the non-resolved expression to find this pattern.

# Polymorphism in more details
